---
# IMPORTANT: Change settings here, but DO NOT change the spacing.
# Remove comments and add values where applicable.
# The descriptions below should be self-explanatory

title: "Question 4: Billionaires"
#subtitle: "This will appear as Right Header"

documentclass: "elsarticle"

# --------- Thesis title (Optional - set to FALSE by default).
# You can move the details below around as you please.
Thesis_FP: FALSE
# Entry1: "An unbelievable study with a title spanning multiple lines."
# Entry2: "\\textbf{Some Guy}" # textbf for bold
# Entry3: "A thesis submitted toward the degree of Doctor of Philosophy"
# Uni_Logo: Tex/Logo.png # Place a logo in the indicated location (from your root, e.g. defaults to ~/Tex/Logo.png) and uncomment this line. Leave uncommented for no image
# Logo_width: 0.3 # If using a logo - use this to set width (size) of image
# Entry4: "Under the supervision of: \\vfill Prof. Joe Smith and Dr. Frank Smith"
# Entry5: "Stellenbosch University"
# Entry6: April 2020
# Entry7:
# Entry8:

# --------- Front Page
# Comment: ----- Follow this pattern for up to 5 authors
AddTitle: TRUE # Use FALSE when submitting to peer reviewed platform. This will remove author names.
Author1: "Matthew Thompson"  # First Author - note the thanks message displayed as an italic footnote of first page.
Ref1: "Department of Economics, Stellenbosch University" # First Author's Affiliation
Email1: "22892435\\@sun.ac.za" # First Author's Email address

# Author2: "John Smith"
# Ref2: "Some other Institution, Cape Town, South Africa"
# Email2: "John\\@gmail.com"
# CommonAffiliation_12: TRUE # If Author 1 and 2 have a common affiliation. Works with _13, _23, etc.
# 
# Author3: "John Doe"
# Email3: "Joe\\@gmail.com"
# 
# CorrespAuthor_1: TRUE  # If corresponding author is author 3, e.g., use CorrespAuthor_3: TRUE
# 
# # Comment out below to remove both. JEL Codes only given if keywords also given.
# keywords: "Multivariate GARCH \\sep Kalman Filter \\sep Copula" # Use \\sep to separate
# JELCodes: "L250 \\sep L100"

# ----- Manage headers and footers:
#BottomLFooter: $Title$
#BottomCFooter:
#TopLHeader: \leftmark # Adds section name at topleft. Remove comment to add it.
BottomRFooter: "\\footnotesize Page \\thepage" # Add a '#' before this line to remove footer.
addtoprule: TRUE
addfootrule: TRUE               # Use if footers added. Add '#' to remove line.

# --------- page margins:
margin: 2.3 # Sides
bottom: 2 # bottom
top: 2.5 # Top
HardSet_layout: TRUE # Hard-set the spacing of words in your document. This will stop LaTeX squashing text to fit on pages, e.g.
# This is done by hard-setting the spacing dimensions. Set to FALSE if you want LaTeX to optimize this for your paper.

# --------- Line numbers
linenumbers: FALSE # Used when submitting to journal

# ---------- References settings:
# You can download cls format here: https://www.zotero.org/ - simply search for your institution. You can also edit and save cls formats here: https://editor.citationstyles.org/about/
# Hit download, store it in Tex/ folder, and change reference below - easy.
bibliography: Tex/ref.bib       # Do not edit: Keep this naming convention and location.
csl: Tex/harvard-stellenbosch-university.csl # referencing format used.
# By default, the bibliography only displays the cited references. If you want to change this, you can comment out one of the following:
#nocite: '@*' # Add all items in bibliography, whether cited or not
# nocite: |  # add specific references that aren't cited
#  @grinold2000
#  @Someoneelse2010

# ---------- General:
RemovePreprintSubmittedTo: TRUE  # Removes the 'preprint submitted to...' at bottom of titlepage
#Journal: "Journal of Finance"   # Journal that the paper will be submitting to, if RemovePreprintSubmittedTo is set to TRUE.
toc: FALSE                       # Add a table of contents
numbersections: TRUE             # Should sections (and thus figures and tables) be numbered?
fontsize: 11pt                  # Set fontsize
linestretch: 1.2                # Set distance between lines.
link-citations: TRUE            # This creates dynamic links to the papers in reference list.

### Adding additional latex packages:
# header-includes:
#    - \usepackage{colortbl} # Add additional packages here.

output:
  pdf_document:
    keep_tex: TRUE
    template: Tex/TexDefault.txt
    fig_width: 3.5 # Adjust default figure sizes. This can also be done in the chunks of the text.
    fig_height: 3.5
#abstract: |
  #Abstract to be written here. The abstract should not be too long and should provide the reader with a good understanding what you are writing about. Academic papers are not like novels where you keep the reader in suspense. To be effective in getting others to read your paper, be as open and concise about your findings here as possible. Ideally, upon reading your abstract, the reader should feel he / she must read your paper in entirety.
---

<!-- First: Set your default preferences for chunk options: -->

<!-- If you want a chunk's code to be printed, set echo = TRUE. message = FALSE stops R printing ugly package loading details in your final paper too. I also suggest setting warning = FALSE and checking for warnings in R, else you might find ugly warnings in your paper. -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.width = 6, fig.height = 5, fig.pos="H", fig.pos = 'H')
# Note: Include = FALSE implies the code is executed, but not printed in your pdf.
# warning and message = FALSE implies ugly messages and warnings are removed from your pdf.
# These should be picked up when you execute the command chunks (code sections below) in your rmd, not printed in your paper!

# Lets load in example data, and see how this can be stored and later called from your 'data' folder.
if(!require("tidyverse")) install.packages("tidyverse")
library(tidyverse)


billionaires <- read_csv("./data/Billions/billionaires.csv")

list.files('code/', full.names = T, recursive = T) %>%
    .[grepl('.R', .)] %>% 
    as.list() %>% 
    walk(~source(.))
```


<!-- ############################## -->
<!-- # Start Writing here: -->
<!-- ############################## -->

# Introduction \label{Introduction}


To tackle this problem, we investigate a few relationships found in the data. The first one we'd like to examine is the claim that the US has more new billionaires who came from entrepreneurial success vs in other developed and emerging economies where there tends to be more inherited wealth.


# Entrepreneurial spirit in US vs Others

We start by examining the United States billionaire landscape on its own, checking to see how many of the billionaires came from entrepreneurship and how many came from inherited wealth.  
First want to extract US billionaires only.

```{r Only US}
US_billion <- US_billion_extract("United States")
```

After that, want to compare their sources of wealth and how it changed over the 3 time periods. For each period, want to calculate the proportion of wealth that was inherited and that which was not inherited.

```{r US source of wealth}
US_inherited_prop <- inherited_proportion(US_billion)
```
We use a simple pie chart to display the change in proportion of those who inherited wealth over the 3 time periods.

```{r}
fig1 <- plot_pie_inherited(US_inherited_prop)

ggsave("./output/fig1.pdf", fig1, width = 10, height = 6)
ggsave("./Question_4/output/fig1.png", fig1, width = 10, height = 6)
```

```{r, out.width="80%", fig.align="center", fig.cap="Pie chart showing proportions of US billionaires that had inherited vs those that did not inherit their wealth \\label{Fig1}"}
knitr::include_graphics("./output/fig1.pdf")
```

The following table also shows how even though the proportion of inherited wealth has decreased relative to non-inherited sources, the number of billionaires who have inherited their wealth has increased.

```{r US inheritance table}
simple_inheritance_table(US_inherited_prop, caption = "Table showing the US inheritance statistics \\label{tab1}", format = "latex")
```

This leads us to investigate what entrepreneurial spirit and inherited wealth looks like in countries outside of the United States.  
We begin again by extracting all the billionaires from outside of the US.

```{r Outside US billionaires}
outsideUS_billion <- outsideUS_billion_extract()
```
Then we obtain the proportion of this group that have inherited their wealth vs those that have not.

```{r Outside US billionaire inherited proportion}
outsideUS_inherited_prop <- inherited_proportion(outsideUS_billion)
```

```{r Plot Outside US pie chart}
fig2 <- plot_pie_inherited(outsideUS_inherited_prop)

ggsave("./output/fig2.pdf", fig2, width = 10, height = 6)
ggsave("./Question_4/output/fig2.png", fig2, width = 10, height = 6)
```

```{r, out.width="80%", fig.align="center", fig.cap="Pie chart showing proportions of those outside of the US billionaires that had inherited vs those that did not inherit their wealth \\label{Fig2}"}
knitr::include_graphics("./output/fig2.pdf")
```

```{r Outside US inheritance table}
simple_inheritance_table(outsideUS_inherited_prop, caption = "Table showing Outside of the US inheritance statistics \\label{tab2}", format = "latex")
```
Figure \ref{Fig2} shows us that while there was a decrease in the proportion of those who obtained their wealth from non-inheritance over 1996-2001, a large increase in this proportion occurred over 2001-2014. Note also how in each period the proportion of those who made their wealth from non-inheritance is greater than half of the population of billionaires outside of the US. This contradicts the statement saying that outside the US houses billionaires who've mostly sourced their wealth from inheritance. 


Tables \ref{tab1} and \ref{tab2} show how even though the US has a slightly higher proportion over time of those billionaires who had not inherited their wealth which had increased over the time periods, those from outside of the US also experienced a decrease in proportion of the number of wealthy coming from inheritance.
```{r Growth calculations}
growth_US <- growth_in_count(US_inherited_prop)

growth_outsideUS <- growth_in_count(outsideUS_inherited_prop)
```

A simple calculation shows that the growth rate for those who have inherited wealth in the US is `r round(growth_US$growth_inherited[2], 1)`% for 2001 and `r round(growth_US$growth_inherited[3], 1)`% over 2014, and `r round(growth_US$growth_not_inherited[2], 1)`% and `r round(growth_US$growth_not_inherited[3], 1)`% for those who have not inherited wealth. These same rates for those outside of the US are `r round(growth_outsideUS$growth_inherited[2], 1)`% for 2001 and `r round(growth_outsideUS$growth_inherited[3], 1)`%, and `r round(growth_outsideUS$growth_not_inherited[2], 1)`% and `r round(growth_outsideUS$growth_not_inherited[3], 1)`%. What these figures show is that those from outside of the US have experienced the largest growth rate in the number of new billionaires who have not come from inherited wealth. This contradicts the first statement, showing that there may be a stronger entrepreneurial spirit displayed by those from outside of the US in more recent years, seen with the higher growth rate when compared to that of the US over 2001-2014.

# Sector analysis

This section lays out the analysis of the second statement that most new-made millionaires are in software, compared to consumer services type industries of the 90s.  

Here I created a plot showcasing the top 10 billionaire sectors while using number of billionaires in software as a measuring device. 

```{r}
fig3 <- plot_sectors(billionaires)

ggsave("./output/fig3.pdf", fig3, width = 12, height = 6)
```

```{r, out.width="80%", fig.align="center", fig.cap="Column plots showing the top 10 billionaire sectors over the 3 periods, using the number of software billionaires as a benchmark in each \\label{Fig3}"}
knitr::include_graphics("./output/fig3.pdf")
```


Figure \ref{Fig3} shows that the second statement is also not valid. Clearly, the number of billonaires in the software sector are lagging behind many sectors such as real estate, retail, construction, media, banking, pharmaceuticals and hedge funds.  
To evaluate the second part of this statement we include GDP per country in the analysis. This entails using a simple linear regression to model if coming from a richer country increases or decreases the probability of the billionaire being part of the software sector.

```{r}
linear_reg_software_gdp(billionaires, caption = "Table showing results of regression of log of GDP on the probability of being in the software sector \\label{tab3}")
```

Table \ref{tab3} also shows contradictory information to the second statement made. It shows that there is a very small and positive insignificant linear relationship between GDP and the probability of a billionaire being in the software sector, after including for time controls. 


# Conclusion

Through the various plots and tables provided, I have shown evidence that both claims made are unfounded. 

@fama1997


<!-- Make title of bibliography here: -->
<!-- \newpage -->

\newpage

# References {-}

<div id="refs"></div>


# Appendix {-}

## Appendix A {-}

Some appendix information here

## Appendix B {-}

