---
title: "Netflix"
documentclass: elsarticle
Thesis_FP: false
output:
  pdf_document:
    keep_tex: true
    template: Tex/TexDefault.txt
    fig_width: 3.5
    fig_height: 3.5
  html_document:
    df_print: paged
Author1: Matthew Thompson
Ref1: Department of Economics, Stellenbosch University
Email1: 22892435\@sun.ac.za
BottomRFooter: \footnotesize Page \thepage
addtoprule: true
addfootrule: true
margin: 2.3
bottom: 2
top: 2.5
HardSet_layout: true
linenumbers: false
bibliography: Tex/ref.bib
csl: "Tex/harvard-stellenbosch-university.csl"
RemovePreprintSubmittedTo: true
Journal: Journal of Finance
toc: false
numbersections: true
fontsize: 11pt
linestretch: 1.2
link-citations: true
AddTitle: true
---

<!-- First: Set your default preferences for chunk options: -->

<!-- If you want a chunk's code to be printed, set echo = TRUE. message = FALSE stops R printing ugly package loading details in your final paper too. I also suggest setting warning = FALSE and checking for warnings in R, else you might find ugly warnings in your paper. -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.width = 6, fig.height = 5, fig.pos="H", fig.pos = 'H')

if(!require("tidyverse")) install.packages("tidyverse")
library(tidyverse)

list.files('code/', full.names = T, recursive = T) %>%
    .[grepl('.R', .)] %>% 
    as.list() %>% 
    walk(~source(.))
```

```{r Read data}
Titles <- read_rds("./data/netflix/titles.rds")
Credits <- read_rds("./data/netflix/credits.rds")
Movie_Info <- read_csv("./data/netflix/netflix_movies.csv")
```


<!-- ############################## -->
<!-- # Start Writing here: -->
<!-- ############################## -->

# Introduction \label{Introduction}

To tackle this problem, we set about comparing the most popular genres of movie and shows in every country (by frequency). We then look at which movie producing countries create the most movies, and which of them produce the best quality movies according to ratings.


# Genres and IMDB ratings

First we need to split the genres so that there is one observation of genre per row.

```{r Get genres}

Titles_clean <- one_genre_titles(Titles)

Movie_Info_clean <- one_genre_mov_info(Movie_Info)
```

Now want to make sure that all genre entries match in both dataframes. Do this by changing entries in the `Titles_clean` dataframe to match those from the `Movie_info_clean` dataframe.

```{r}
Titles_clean <- clean_titles_genre(Titles_clean)
```


Now want to compare the different genres and their ratings over time.

```{r}
fig1 <- plot_genre_ratings(Titles_clean)

#ggsave("./output/fig1.pdf", fig1, width = 10, height = 6)
#ggsave("./Question_3/output/fig1.png", fig1, width = 10, height = 6)
```

```{r, out.width="80%", fig.align="center", fig.cap="Density ridges of Netflix genres and their IMDB ratings \\label{Fig1}"}
knitr::include_graphics("./output/fig1.pdf")
```

Top 3 genres of movies/shows in terms of average ratings according to Figure \ref{Fig1} are:

1. History / War (7.1 rating)
2. Documentaries (7.0 rating)

# Country Analysis

To start the country analysis, the country column in the `Titles_clean` dataframe had to be cleaned up to be used in analysis.

```{r clean Countries}
titles_clean_countries <- clean_titles_countries(Titles_clean)
```

After having achieved this, we can now ask which countries produced the movies with the highest average ratings. We shall average the IMDB ratings across all movies created by a country before plotting the top 10 averages.

```{r}
top_10 <- top_10_country_producers(titles_clean_countries)
```

The plot below visualises the top 10 movie producers.

```{r}
fig2 <- plot_top_10(top_10)

#ggsave("./output/fig2.pdf", fig2, width = 12, height = 6)
#ggsave("./Question_3/output/fig2.png", fig2, width = 12, height = 6)
```

```{r, out.width="80%", fig.align="center", fig.cap="Top 10 Movie Producing Countries \\label{Fig2}"}
knitr::include_graphics("./output/fig2.pdf")
```

Taking these top 10 countries, we now want to see what the average rating of each is. 

```{r}
fig3 <- plot_join_averages_top10(top_10)

#ggsave("./output/fig3.pdf", fig3, width = 10, height = 6)
#ggsave("./Question_3/output/fig3.png", fig3, width = 10, height = 6)
```

```{r, out.width="80%", fig.align="center", fig.cap="Movie quantity vs quality by country for top 10 producers \\label{Fig3}"}
knitr::include_graphics("./output/fig3.pdf")
```

Figure \ref{Fig3} tells the story that while the United States has produced the most number of movies, its average rating lies below that of four countries, namely: South Korea, Japan, China, and Great Britain. South Korea produces the highest quality movie on average according to IMDB ratings.

# Conclusion

The analysis has shown that History and War films, followed by documentaries are the most-loved across the world. Furthermore, while the United States produces the most movies/shows, it is South Korea that produces the subjective best of them.


<!-- Make title of bibliography here: -->
<!-- \newpage -->

\newpage



<!-- <div id="refs"></div> -->




